### 2015-12-02 paper.tex
Consistency in Re_c definition

\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at blade tip, root,
    and mid-span, corresponding to various tow speeds at $\lambda=3.1$.}

@@

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda c U_\infty/
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. The tendency of $C_P$ to continue increasing slightly could be
an effect of lower virtual camber when compared to the strong $Re$-independence
of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.

>>>>

\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
blade chord Reynolds numbers $Re_c \equiv \lambda U_\infty c / \nu$ at blade
tip, root, and mid-span, corresponding to various tow speeds at $\lambda=3.1$.}

@@

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. The tendency of $C_P$ to continue increasing slightly could be
an effect of lower virtual camber when compared to the strong $Re$-independence
of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
